---
title: "Quick Start"
author: "Douglas Ashton"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Intro paragraph

## Aggregated Data

Data comes in in a summed up way. Either load an example data set or make a matrix and sum it.

```{r}
constraints <- matrix(rep(c(10,6,6,4,2,1),2),ncol=2)
```

## Creating a network

```{r}
library(banknet)
set.seed(11)
fit <- unsum(constraints, 12)
fit$AW
```

Run through unsum and a few easy options. One with all the defaults, one with a few more options set.

## Maximum Entropy Solution

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold', fig.cap="hello"}
library(igraph)
g <- graph.adjacency(fit$AW, weighted = TRUE)
lo <- layout.circle(g)
plot(g, edge.width=E(g)$weight, edge.curved=is.mutual(g), layout=lo)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## Doug Remove

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

